### 2015-03-27 markdown/manuscript.tex
forgot to render

In this contribution we must face the fact that \emph{this response is inevitable}. Not just from silly lay ``customers'' in an application project, but from ourselves. Whether the project is ``theoretical'' or ``practical''. Whether it is ``small'' or ``large''.

>>>>

In this contribution we must face the fact that such a response is inevitable: not just from silly lay ``customers'' in an application project, but from ourselves; whether the project is ``theoretical'' or ``practical''; whether it is ``small'' or ``large''. Projects resist our initial plans.
